Paper Analysis

### 2024-10-16 Paper_WriteUp/Paper_Plots.qmd
update many of the plots and add a new template. trying to tidy up the plotting code

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(here)

options(mc.cores = parallel::detectCores())

theme_set(theme_bw())

@@

all_data_path <- rep(NA, 4)
all_data_path[1] <- here("box_data/lichess1700-1900/")
all_data_path[2] <- here("box_data/lichess2000-2200/")
all_data_path[3] <- here("box_data/lichess2300-2500/")
all_data_path[4] <- here("box_data/lichessGrandmasters/")

res_data_path <- rep(NA, 4)
res_data_path[1] <- here("results/lichess1700-1900/")
res_data_path[2] <- here("results/lichess2000-2200/")
res_data_path[3] <- here("results/lichess2300-2500/")
res_data_path[4] <- here("results/lichessGrandmasters/")

@@

lichess_data <- files %>% 
  map_dfr(~read_player(data_path, .x))

@@

bullet_data <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("rated bullet game", Event))

@@

blitz_data <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "180+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("rated blitz game", Event))

@@

lichess_data_gm <- files %>% 
  map_dfr(~read_player(data_path, .x))

@@

bullet_data_gm <- lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("rated bullet game", Event))

@@

blitz_data_gm <- lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "180+0") %>%
  filter(Variant == "Standard") %>%
  filter(grepl("rated blitz game", Event))

@@

# Apply function to each group
result_blitz <- outcomes_blitz %>%
  summarise(session_length = list(get_true_sequences(less_7_min)))

@@

global_17_19_bullet_prev <- fit_17_19_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name, ncol = 4, scales = "free") +
  labs(x = element_blank(), y = element_blank()) +
  theme_4col() +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

player_pars <- fit_17_19_bullet_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id")

@@

@@

global_gm_bullet_prev <- fit_gm_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name, ncol = 4, scales = "free") +
  labs(x = element_blank(), y = element_blank()) +
  theme_4col() +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

@@

player_pars <- fit_gm_bullet_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id")

@@

## then the winner effects plot
winner_plot_gm <- player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~player_name, scales = "free", ncol = 5) +
  theme_5col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

indiv_plot_gm <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~player_name, scales = "free", ncol = 5) +
  theme_5col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

prev_pars <- fit_gm_bullet_prev$draws(c("mu_beta",
                                        "gamma1", "gamma2",
                                        "sigma_1", "tau[1]",
                                        "tau[2]",
                                        "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Prev. Game")

pre_10_pars <- fit_gm_bullet_10$draws(c("mu_beta",
                                        "gamma1", "gamma2",
                                        "sigma_1", "tau[1]",
                                        "tau[2]",
                                        "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Prev. 10 Games")

hist_comp_global <- bind_rows(prev_pars, pre_10_pars) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(name), scales = "free") +
  theme_8col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

hist_comp_global

ggsave(plot = hist_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_global.png")), dpi = 600,
       height = 4, width = 7)

@@

player_pars_pre <- fit_gm_bullet_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. Game")

player_pars_pre_10 <- fit_gm_bullet_10$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. 10 Games")

hist_comp_winner <- bind_rows(player_pars_pre, player_pars_pre_10) |> 
  filter(id < 7) |> 
  filter(param == 2) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

## then player effects
hist_comp_player <- bind_rows(player_pars_pre, player_pars_pre_10) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

```{r bullet v blitz for 17-19}

data_path <- here("results/lichess1700-1900")

@@

bul_blit_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(name), scales = "free") +
  theme_8col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

@@

player_pars_bullet <- fit_17_19_bullet_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

player_pars_blitz <- fit_17_19_blitz_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Blitz")

@@

fit_gm_bullet_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_bullet_model_prev.RDS"))

fit_gm_blitz_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_blitz_model_prev.RDS"))

blitz_gm <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))

bullet_pars <- fit_gm_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Bullet")

blitz_pars <- fit_gm_blitz_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Blitz")

bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(name), scales = "free") +
  theme_8col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

@@

ggsave(plot = bul_blit_gm_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_global.png")), dpi = 600,
       height = 4, width = 7)

@@

player_pars_bullet <- fit_gm_bullet_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

player_pars_blitz <- fit_gm_blitz_prev$draws() %>% 
  as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Blitz")

comp_gm_winner <- bind_rows(player_pars_bullet, player_pars_blitz) |> 
  filter(id < 7) |> 
  filter(param == 2) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

comp_gm_player <- bind_rows(player_pars_bullet, player_pars_blitz) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

global_winner <- as_draws_df(fit_17_19_first$draws(variables = "mu_beta")) %>% 
  rename("Initial Games" = mu_beta) %>% 
  bind_cols(as_draws_df(fit_17_19_last$draws(variables = "mu_beta")) %>% 
              rename("Later Games" = mu_beta)) %>% 
  select(`Initial Games`, `Later Games`) %>% 
  pivot_longer(cols = everything()) %>% 
  ggplot(aes(value, fill = name)) +
  geom_histogram(position = "identity") +
  facet_wrap(~name, ncol = 1) +
  labs(fill = element_blank(), y = element_blank(), x = element_blank()) +
  theme(legend.position = "none",
        axis.text = element_text(size = axis_text_size),
        axis.title = element_text(size = axis_title),
        legend.text = element_text(size = legend_text),
        strip.text = element_text(size = axis_title),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = title_size)) +
  # labs(title = "Selected 1700-1900 Bullet Players") +
  NULL

@@

users <- readRDS(file = here(data_path, "time", "select_users_bullet.RDS"))
## indiv winner effects
random_effect_first <- fit_17_19_first$draws() %>% as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) %>% 
  mutate(when = "Initial")

random_effect_last <- fit_17_19_last$draws() %>% as_draws_df() %>%
  select(starts_with("beta[")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) %>% 
  mutate(when = "Later")

betas <- bind_rows(random_effect_first, random_effect_last) %>% 
  select(value, param, id, when)

@@

betas %>% left_join(player_id, by = "id") %>% 
  mutate(player = factor(player, levels = users))

>>>>

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(viridis)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

all_data_path <- rep(NA, 4)
all_data_path[1] <- here("box_data/lichess1700-1900/")
all_data_path[2] <- here("box_data/lichess2000-2200/")
all_data_path[3] <- here("box_data/lichess2300-2500/")
all_data_path[4] <- here("box_data/lichessGrandmasters/")
res_data_path <- rep(NA, 4)
res_data_path[1] <- here("results/lichess1700-1900/")
res_data_path[2] <- here("results/lichess2000-2200/")
res_data_path[3] <- here("results/lichess2300-2500/")
res_data_path[4] <- here("results/lichessGrandmasters/")

@@

lichess_data <- files |> 
  map_dfr(~read_player(data_path, .x))

@@

bullet_data <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0") |>
  filter(Variant == "Standard") |>
  filter(grepl("rated bullet game", Event))

@@

blitz_data <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "180+0") |>
  filter(Variant == "Standard") |>
  filter(grepl("rated blitz game", Event))

@@

lichess_data_gm <- files |> 
  map_dfr(~read_player(data_path, .x))

@@

bullet_data_gm <- lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "60+0") |>
  filter(Variant == "Standard") |>
  filter(grepl("rated bullet game", Event))

@@

blitz_data_gm <- lichess_data_gm |> 
  mutate(Event = tolower(Event)) |>
  filter(TimeControl == "180+0") |>
  filter(Variant == "Standard") |>
  filter(grepl("rated blitz game", Event))

@@

# Apply function to each group
result_blitz <- outcomes_blitz |>
  summarise(session_length = list(get_true_sequences(less_7_min)))

@@

facet_labels <- as_labeller(c(
  mu_beta = "mu[beta]",
  gamma1 = "gamma[1]",
  gamma2 = "gamma[2]",
  sigma_1 = "sigma[1]",
  `tau[1]` = "tau[1]",
  `tau[2]` = "tau[2]",
  sigma_g1 = "sigma[g[1]]",
  sigma_g2 = "sigma[g[2]]"
), label_parsed)

global_17_19_bullet_prev <- fit_17_19_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name, ncol = 4, scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank()) +
  theme_4col() +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

player_pars <- fit_17_19_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id")

@@

```{r new boxplots}

winner_plot_17_19 <- player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated W/L-Effect", y = element_blank(), 
       title = "1700-1900 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank()) +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

global_gm_bullet_prev <- fit_gm_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  ggplot(aes(value)) +
  geom_histogram() +
   facet_wrap(~name, ncol = 4, scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank()) +
  theme_4col() +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

@@

player_pars <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id")

@@

## then the winner effects plot
winner_plot_gm <- player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated W/L-Effect", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

indiv_plot_gm <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

prev_pars <- fit_gm_bullet_prev$draws(c("mu_beta",
                                        "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "Prev. Game")

pre_10_pars <- fit_gm_bullet_10$draws(c("mu_beta",
                                        "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "Prev. 10 Games")

hist_comp_global <- bind_rows(prev_pars, pre_10_pars) |> 
  ggplot(aes(x = value, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

ggsave(plot = hist_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_global.png")), dpi = 600,
       height = 3.5, width = 7)

@@

player_pars_pre <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. Game")

player_pars_pre_10 <- fit_gm_bullet_10$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. 10 Games")

hist_comp_winner <- player_pars_pre |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_pre_10 |> filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

## then player effects
## should update this also
hist_comp_player <- bind_rows(player_pars_pre, player_pars_pre_10) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

```{r bullet v blitz for 17-19}
data_path <- here("results/lichess1700-1900")

@@

bul_blit_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(name), scales = "free",
              labeller = labeller(name = facet_labels)) +
  theme_8col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

@@

## then repeat for winner and player effects
player_pars_bullet <- fit_17_19_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

player_pars_blitz <- fit_17_19_blitz_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Blitz")

@@

fit_gm_bullet_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_bullet_model_prev.RDS"))
bullet_gm <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))
fit_gm_blitz_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_blitz_model_prev.RDS"))
blitz_gm <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))
## compare global effects first
bullet_pars <- fit_gm_bullet_prev$draws(c("mu_beta",
                                          "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "Bullet")

blitz_pars <- fit_gm_blitz_prev$draws(c("mu_beta",
                                        "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "Blitz")

bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

ggsave(plot = bul_blit_gm_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_global.png")), dpi = 600,
       height = 3.5, width = 7)

@@

player_pars_bullet <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

player_pars_blitz <- fit_gm_blitz_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Blitz")

comp_gm_winner <- player_pars_bullet |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "D")

@@

## TO DO - this needs to be updated
comp_gm_player <- bind_rows(player_pars_bullet, player_pars_blitz) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

global_winner <- as_draws_df(fit_17_19_first$draws(variables = "mu_beta")) |> 
  rename("Initial Games" = mu_beta) |> 
  bind_cols(as_draws_df(fit_17_19_last$draws(variables = "mu_beta")) |> 
              rename("Later Games" = mu_beta)) |> 
  select(`Initial Games`, `Later Games`) |> 
  pivot_longer(cols = everything()) |> 
  ggplot(aes(value, fill = name)) +
  geom_histogram(position = "identity") +
  facet_wrap(~name, ncol = 1) +
  labs(fill = element_blank(), y = element_blank(), x = element_blank()) +
  theme(legend.position = "none",
        axis.text = element_text(size = axis_text_size),
        axis.title = element_text(size = axis_title),
        legend.text = element_text(size = legend_text),
        strip.text = element_text(size = axis_title),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = title_size)) +
  # labs(title = "Selected 1700-1900 Bullet Players") +
  NULL

@@

users <- readRDS(file = here(data_path, "time", "select_users_bullet.RDS"))
## indiv winner effects
random_effect_first <- fit_17_19_first$draws() |> as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(when = "Initial")

random_effect_last <- fit_17_19_last$draws() |> as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(when = "Later")

betas <- bind_rows(random_effect_first, random_effect_last) |> 
  select(value, param, id, when)

@@

betas |> left_join(player_id, by = "id") |> 
  mutate(player = factor(player, levels = users))

winner_effect_plot <- betas |> 
  left_join(player_id, by = "id") |> 
  mutate(player = factor(player, levels = users)) |> 
  filter(param == 2) |> 
  mutate(id = factor(id, levels = c(1:10))) |> 
  ggplot(aes(value, fill = when)) +
  geom_histogram() +
  geom_vline(xintercept = 0, alpha = 0.5) +
  scale_x_continuous(breaks = c(-0.25, 0.25)) +
  # xlim(c(-1.5, 1.5)) +
  facet_grid(rows = vars(when), cols = vars(player), scales = "free_x") +
  labs(fill = element_blank(), y = element_blank(), 
       # title = "Individual Winner Effects, Selected 1700-1900 Bullet Players",
       x = element_blank()) +
  theme_10col()
  # theme(axis.ticks.y = element_blank(),
  #       axis.text.y = element_blank(),
  #       axis.text = element_text(size = axis_text_size - 4),
  #       axis.title = element_text(size = axis_title),
  #       legend.text = element_text(size = legend_text),
  #       strip.text = element_text(size = axis_title - 6),
  #       legend.position = "none",
  #       plot.title = element_text(size = title_size))
